A meta-analysis of mental rotation ability in the first years of life

### 2022-04-29 code/analysis.Rmd
Correct heterogeneity and ICC estimates

# Compute intra-class correlation
sd_article <- VarCorr(res_brm)$article$sd
sd_experiment <- VarCorr(res_brm)$`article:experiment`$sd
(icc <- sd_article / (sd_article + sd_experiment))

>>>>

# Compute by-experiment variance
sd_experiment_draws <- as.matrix(
  res_brm,
  variable = "sd_article:experiment__Intercept"
)
mean_qi(sd_experiment_draws^2)

# Compute by-article variance
sd_article_draws <- as.matrix(
  res_brm,
  variable = "sd_article__Intercept"
)
mean_qi(sd_article_draws^2)

# Compute intra-class correlation
icc_draws <- sd_article_draws^2 / (sd_article_draws^2 + sd_experiment_draws^2)
mean_qi(icc_draws)
